Prediction of 2024 US election ...

### 2024-10-22 paper/paper.qmd
update simulate data

---
title: "Prediction of US election with linear model"
author: 
  - Colin Sihan Yang
  - Lexun Yu
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/yulexun/uselection](https://github.com/yulexun/uselection)."
date: today
date-format: long
abstract: "This paper forecast the winner of the upcoming US presidential election using “poll-of-polls” by building a linear model."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Prediction of 2024 US election ..."
author: 
  - Colin Sihan Yang
  - Lexun Yu
  - Siddharth Gowda
thanks: "Code and data are available at: [https://github.com/yulexun/uselection](https://github.com/yulexun/uselection)."
date: today
date-format: long
abstract: "We forecast the winner of the 2024 US presidential election using “poll-of-polls” by building a linear model."
format: pdf
number-sections: true
bibliography: references.bib
---
